\documentclass[9pt]{extarticle}
\usepackage{url,parskip,tabularx}
\usepackage{lipsum}
\usepackage[margin=0.3in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{ifthen}

\renewcommand{\familydefault}{\sfdefault}

\newcommand{\reference}[5]{
    \textbf{#1} \newline
    {\footnotesize #2} \newline
    #3 \newline
    \href{mailto:#4}{#4} \newline
    #5 \newline
}

\newcommand{\skills}[2]{
    \textbf{#1} \newline
    #2
}

\newcommand{\entry}[3]{
    \textbf{#1} \newline
    {\footnotesize #2}
    \ifthenelse{\equal{#3}{\null}}{}
    {
        \begin{flushleft}
            #3
        \end{flushleft}
    }
}

\titleformat{\section}{\Large\raggedright\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
\titleformat{\subsection}{\Large\raggedright}{}{1em}{}
\titlespacing{\subsection}{0pt}{3pt}{3pt}

\begin{document}

\pagestyle{empty} 

\begin{minipage}[t]{.30\textwidth}
\vspace*{0pt}

\begin{center}
{\huge \bfseries James Barnes\par}
\end{center}

\bigskip
\hrule
\bigskip

\begin{center}
Geelong, Victoria, Australia \\
\href{mailto:jamesbarnes2505@gmail.com}{jamesbarnes2505@gmail.com} \\
+61 467 093 491 \\
\href{http://github.com/jimbxb}{github.com/jimbxb}
\end{center}

\bigskip
\hrule
\bigskip

\section{Summary}

\begin{flushleft}
I am a student of computer science, completing a Master of Computer Science at The University of Melbourne. 
My research project in the Master of Computer Science degrees relates to the design ad implementation of a higher order extension 
to a programming language called Wybe, and features various novel compiler optimisations.
Recently, I completed a Bachelor of Science achieving excellent results.
My strengths and interests relate to computing and technology.
\end{flushleft} 

\medskip

\section{Skills}

\skills{Programming Languages:}
{C, Java, Python, JavaScript, Haskell, Prolog, MATLAB, {\fontfamily{cmr}\selectfont \LaTeX{}}, HTML5, CSS. \newline }

\skills{Software:}
{Visual Studio Code, Github, Eclipse, Microsoft Word, Microsoft Excel, Microsoft PowerPoint. \newline }

\skills{Natural Languages:}
{Native English, introductory-level Chinese (Mandarin).}

\medskip

\section{References}

\reference{Professor Timothy Baldwin}
{The University of Melbourne}
{Melbourne Laureate Professor}
{tb@ldwin.net}
{+61 3 8344 1363}

\reference{Michael Broeks}
{WorkSafe Victoria}
{Workers' Compensation (Premium) \\ -- Product Owner}
{michael\_broeks@worksafe.vic.gov.au}
{+61 4 1113 2922}

\reference{Les Kitchen}
{The University of Melbourne}
{Honorary Senior Research Fellow}
{jebref@po.ljk.id.au}
{}

\end{minipage}\hfill
\begin{minipage}[t]{.65\textwidth}
\vspace*{0pt}

\section{Education}

\entry{The University of Melbourne, Master of Computer Science}
{2020 - Present}
{
    \textbf{Topic:} Higher-order Programming in Wybe \newline
    \textbf{Grade:} First Class Honours (83.000 WAM) \newline
}

\entry{The University of Melbourne, Bachelor of Science}
{2017 - 2019}
{
    \textbf{Major:} Computing and Software Systems \newline
    \textbf{Grade:} First Class Honours (83.000 WAM) \newline
}

\entry{Belmont High School}
{2011 - 2016}
{Select-Entry Accelerated Learning Program}

\medskip

\section{Work Experience}

\entry{Summer Vacation Intern -- Telstra}
{Summer 2020 - 2021}
{
    My role as an intern at Telstra was primarily focused around the the MyTelstra app.
    I was responsible for the synthesis and maintenance of quality assurance tests, along with general devops 
    responsibilities. I also developed features on the front-end of the MyTelstra web app. \newline
}

\entry{Academic Tutor \& Demonstrator -- The University of Melbourne}
{2019 - Present}
{
    My role as a tutor and demonstrator is to teach introductory concepts in computing, primarily to first year students.
    Tutors are also responsible for grading a large number of student's exams and assignments. 
    I also was responsible for facilitating discussion within lectures. \newline
}

\entry{Data Analyst -- WorkSafe Victoria}
{Summer 2019 - 2020}
{
    My role at WorkSafe was the validation and cleaning of confidential and public company records. 
    Extra responsibilities included the validation of automated data entry, making heavy use of macros in Excel. \newline
}

\entry{Kitchen Hand -- Soft Cafe}
{2015 - 2022}
{\null}

\medskip

\section{Projects}

\entry{Scalr.io -- UniHack'21 1st Place}
{2021}
{
    First-prize winning UniHack'21 submission built with my team over the course of 48 hours. 
    Scalr.io offers a platform where users can upload and utilise machine learning models through a simple to use web interface or API,
    allowing users with little technical knowledge to utilise machine learning. \newline
}

\entry{Airloom -- B.S. Capstone Project}
{2019, Semester 2}
{
    Undergraduate degree capstone project, built over the course of a semester. The project involved rigorous software modelling,
    planning, design and implementation of a web-based family heirloom register, making use of various technologies.
}

\medskip

\section{Volunteering}

\entry{Student Representative -- The University of Melbourne}
{
    2022, Semester 1 -- Master of Computer Science. \\
    2021, Semester 1 -- Distributed Algorithms (COMP90020) \\
    2020, Semester 2 -- Advanced Theoretical Computer Science (COMP90057)
}
{
    Student-teacher liaison responsibilities.
}

\medskip

\section{Awards}

\entry{Undergraduate Excellence in Computing and Information Systems Scholarship -- Runner-up}
{2018} 
{
    Awarded to an undergraduate student in the Computing and Software Systems major for excellent academic achievements.
}

\end{minipage}

\end{document}
